Agda Meets Accelerate

### 2012-07-31 paper/main.tex
Added some related work
I inlined the citations as I haven't got the bib files at the moment.

>>>>

Dependent types for array programming: 
\begin{itemize}
\item "Dependent Types for Distributed Arrays".
Wouter Swierstra and Thorsten Altenkirch. Postproceedings of TFP 2008.
\item "More Dependent Types for Distributed Arrays".
Wouter Swierstra. Accepted for publication in the Journal of Higher-order and Symbolic Computation.
\end{itemize}
This work focuses on describing distribution strategies using dependent types (which is orthogonal to our work). However, to characterise distributions, it also tracks bounds in types.

DML:
\begin{itemize}
\item Xi, Hongwei (March 2007). "Dependent ML: An Approach to Practical Programming with Dependent Types". Journal of Functional Programming 17 (2). [There is a previous ICFP paper co-authored with his advisor Bob Harper.]
\end{itemize}
Extension of ML to track array bounds.

Other embedded array languages:
\begin{itemize}
\item Accelerator: C++ library providing data-parallel GPU programming; subsequent work by Satnam Singh provides an F\# binding (but that was never published as for as I know---double check); the language provides only a small subset of the functionality of Accelerate
\item Copperhead: embedded array language in Python; no static guarantees; performance varied widely in our experiments
\item anything else?
\end{itemize}
